\section{Paragraph}
\subsection{Indent}
{\noindent
This is a paragraph with no indent. \par
\indent
This is a paragraph with indent.}

{\setlength\parindent{4em}
Here is a new paragraph. \par
\addtolength\parindent{2em}
Here is a new paragraph.}

{\hangindent=5pc \hangafter=-2
For the left of the paragraph, indent 5px applied in the first 2 lines of the paragraph, 
which is called ``Hanging indentation''.}

\subsection{Segment Spacing}
{\setlength\parskip{3pt}    % between paragraphs
\setlength\leftskip{4em} \setlength\rightskip{1em}
A new paragraph.}

\subsection{Alignment}
{\raggedright
Left alignment. \par
\raggedleft
Right alignment. \par
\centering
Center alignment.}

\begin{flushleft}
    Left alignment environment.
\end{flushleft}

\begin{flushright}
    Right alignment environment.
\end{flushright}

\begin{center}
    Center alignment environment.
\end{center}

\subsection{Hyphenation}
man\-u\-script set the hyphen

{\sloppy
allow wider blank in paragraph so that forbid hyphenation. \par
\fussy
do not allow wide blank in paragraph so that recover default strict hyphenation.}

\begin{sloppypar}
    environment for allowing wider blank in paragraph so that forbid hyphenation.
\end{sloppypar}

\subsection{Ragged2e}   % must usepackage ragged2e
{\RaggedRight
Left alignment with ragged2e. \par
\RaggedLeft
Right alignment with ragged2e. \par
\Centering
Center alignment with ragged2e. \par
\justifying
Return back to uniform two-end alignment with ragged2e.}

\begin{FlushLeft}
    Left alignment environment with ragged2e.
\end{FlushLeft}

\begin{FlushRight}
    Right alignment environment with ragged2e.
\end{FlushRight}

\begin{Center}
    Center alignment environment with ragged2e.
\end{Center}

\begin{justify}
    Uniform two-end alignment environment with ragged2e.
\end{justify}

\subsection{Lettrine}
\lettrine{T}{he} lettrine can be used for first word sanking.

\subsection{Shapepar}
\heartpar{
    绿草苍苍，白雾茫茫，有位佳人，在水一方。
    绿草萋萋，白雾迷离，有位佳人，靠水而居。
    我愿逆流而上，依偎在她身旁。无奈前有险滩，道路又远又长。
    我愿顺流而下，找寻她的方向。却见依稀仿佛，她在水的中央。
    我愿逆流而上，与她轻言细语。无奈前有险滩，道路曲折无已。
    我愿顺流而下，找寻她的足迹。却见仿佛依稀，她在水中伫立。
}