\section{Fonts}
\subsection{Special Characters}
Accents (重音): 
{\LARGE
    \`o, \'o, \^o, \"o, \~o, \=o, \.o, \u{o}, \v{o}, \H{o}, \t{oo}, \r{o}, \c{o}, \d{o}, \b{o}
}

Variants: 
{\LARGE
    \AA, \aa, \AE, \ae, \OE, \oe, \SS, \ss, \IJ, \ij, \L, \l, \O, \o, \i, \j
}

Symbols: 
{\LARGE
    \S, \dag, \ddag, \P, \copyright, \pounds,                       % also can be used in math mode
    % \yen, \checkmark, \circledR, \maltese,                          % error exists
    \textregistered, \texttrademark, \textbullet
}

Ligature (连字): shelfful, shelf{}ful, shelf\/ful

\subsection{Punctuation}
\subsubsection{Quote}
`hello' ``world'' ``dadadadawjb"

It's wjb's howto.

\subsubsection{Minus}
Hyphen (连字符): X-ray

Number ranges (en dash): 1--2. Also can use $\sim$.

Punctuation dash (em dash) (破折号): I am dadadadawjb---a student.

\subsubsection{Ellipsis}
In the last\ldots.

In the middle $\ldots$ middle.

\subsubsection{Indirect Punctuations}
\#, \$, \%, \&, \{, \}, \_, \textbackslash

\subsection{Digits}
Often used with symbol to use character code, such as
\symbol{90},        % decimal
\symbol{"5A},       % hexadecimal
\symbol{'132},      % octal
\symbol{`Z}         % character

\subsection{Fonts Type}
\subsubsection{Font Family}
\textrm{Roman font family.} {\rmfamily Roman font family.}

\textsf{Sans serif font family.} {\sffamily Sans serif font family.}

\texttt{Typewriter font family.} {\ttfamily Typewriter font family.}

{\CJKfamily{zhhei} 黑体} {\heiti 黑体}

{\CJKfamily{zhsong} 宋体} {\songti 宋体}

{\CJKfamily{zhfs} 仿宋} {\fangsong 仿宋}

{\CJKfamily{zhkai} 楷书} {\kaishu 楷书}

{\lucidasans Lucida Sans font family.}  % must defined by \newfontfamily

{\CJKfamily{kai} 楷体}  % must defined by \setCJKfamilyfont

\subsubsection{Font Shape}
\textup{Upright font shape.} {\upshape Upright font shape.}

\textit{Italic font shape.} {\itshape Italic font shape.}

\textsl{Slanted font shape.} {\slshape Slanted font shape.}

\textsc{Small capitals font shape.} {\scshape Small capitals font shape.}

Italic correction: \par
{\itshape M}M       % slanted overflow
{\itshape M\/}M     % no slanted overflow
\textit{M}M         % no slanted overflow
\textit{M\nocorr}   % slanted overflow

\subsubsection{Font Series}
\textmd{Medium font series.} {\mdseries Medium font series.}

\textbf{Bold extended font series.} {\bfseries Bold extended font series.}

\subsubsection{Uniform Set The Three}
\textnormal{Normal font type.} {\normalfont Normal font type.}

\subsubsection{Emphasize}
This is \emph{emphasized} text.

This is {\em emphasized\/} text.

This is \Emph{more emphasized} text.

\underline{Underline emphasize} is not \underline{uniform} and cannot newline.

\uline{Uline emphasize} is \uline{uniform} and can newline. % must usepackage ulem

\uuline{double uline} \uwave{wave uline} \sout{cross line} \xout{wrong line} \dashuline{dash uline} \dotuline{dot uline}    % must usepackage ulem

\CJKunderline{下划线} \CJKunderdblline{双下划线} \CJKunderwave{下波浪线} \CJKsout{删除线} \CJKxout{错误线} \CJKunderdot{下加点}     % must usepackage xeCJKfntef

\subsubsection{Font Size}
{\tiny tiny} {\scriptsize script size} {\footnotesize footnote size} {\small small} {\normalsize normal size}

{\large large} {\Large larger} {\LARGE even larger} {\huge huge} {\Huge largest}

{\zihao{0} 初号} {\zihao{-0} 小初号}

{\zihao{1} 一号} {\zihao{-1} 小一号} {\zihao{2} 二号} {\zihao{-2} 小二号}

{\zihao{3} 三号} {\zihao{-3} 小三号} {\zihao{4} 四号} {\zihao{-4} 小四号} {\zihao{5} 五号} {\zihao{-5} 小五号} {\zihao{6} 六号} {\zihao{-6} 小六号} {\zihao{7} 七号} {\zihao{8} 八号}